---
title: "Insecure Island Syndrome"
subtitle: "Media Repertoires, Informational Threats, and Social Connectedness in a Fragmented Media System"
author:
  - name: "Mu-Jung Cho | 卓牧融"
    orcid: '0000-0001-5500-6336'
    email: 'mjcho@as.edu.tw'
    affiliations:
      - name: 'RCHSS, Academia Sinica'
  - name: "Chia-Ming Hsu"
    affiliations:
      - name: 'RCHSS, Academia Sinica'
format:
  revealjs:
    template-partials:
      - title-slide.html
    theme: [default, synthwave84-reveal-2.scss]
    width: 1280
    height: 720
    margin: 0.06
    slide-number: c
    incremental: false
    slide-level: 2
    embed-resources: true
execute:
  echo: false
  warning: false
  error: false
occassion: "Taiwan Data Futures 2026"
date: last-modified
editor:
  render-on-save: true
---

```{r}
#| label: setup
#| echo: false
#| cache: false

knitr::opts_chunk$set(dev = "svglite", dev.args = list(bg = "transparent"))

suppressMessages({
  library(tidyverse)
  library(survey)
  library(glue)
  library(forcats)
  library(stringi)
  library(broom)
  library(gt)
})

theme_sw <- function(base_size = 13) {
  ggplot2::theme_minimal(base_size = base_size) +
  ggplot2::theme(
    plot.background  = ggplot2::element_rect(fill = NA, colour = NA),
    panel.background = ggplot2::element_rect(fill = NA, colour = NA),
    legend.background = ggplot2::element_rect(fill = NA, colour = NA),
    text        = ggplot2::element_text(colour = "#f4eee4"),
    axis.text   = ggplot2::element_text(colour = "#f4eee4"),
    axis.title  = ggplot2::element_text(colour = "#f4eee4"),
    panel.grid.major = ggplot2::element_line(colour = "#6d77b3", linewidth = 0.2),
    panel.grid.minor = ggplot2::element_blank()
  )
}

# --- Resolve the export by pinning to the manuscript's own declaration -------------------
# NOT by globbing on the version prefix. Version ordering by string sort is unsound: under
# C collation "_" (0x5F) sorts above "." (0x2E), so a descending sort of
# Analysis_v*_export.RData puts the superseded Analysis_v5_export.RData *ahead* of
# Analysis_v5.3_export.RData, while macOS ICU collation orders them the other way. Which
# export loaded was therefore locale-dependent — a defect regardless of which way it fell.
# The deck now reads the path the manuscript itself declares, so it cannot silently drift
# onto a different export than the paper it is presenting. Hard-fails rather than falling
# back to a glob: a deck built on the wrong export is worse than a deck that will not build.
ms_qmd <- "../../Cho-IIS/Manuscript/Manuscript_v5.3_2026-07-31.qmd"
export_path <- Sys.getenv("IIS_EXPORT", unset = NA_character_)
if (is.na(export_path)) {
  if (!file.exists(ms_qmd)) {
    stop("Cannot pin the export: manuscript not found at ", ms_qmd,
         ". Set IIS_EXPORT to override.")
  }
  .ms_src  <- readLines(ms_qmd, warn = FALSE)
  .pat     <- 'load\\(\\s*"[^"]*Analysis_v[^"]*_export\\.RData"'
  .hits    <- regmatches(.ms_src, regexpr(.pat, .ms_src))
  if (length(.hits) == 0L) {
    stop("Cannot parse a load(...) export path out of ", ms_qmd,
         "'s Setup chunk. The deck pins its export to the manuscript's declaration and ",
         "will not guess. Fix the manuscript or set IIS_EXPORT.")
  }
  if (length(unique(.hits)) > 1L) {
    stop("The manuscript declares more than one export path (",
         paste(unique(.hits), collapse = " | "),
         "). Resolve the ambiguity in the manuscript or set IIS_EXPORT.")
  }
  # The manuscript's path is relative to Manuscript/; rebase it onto this deck's directory.
  .ms_rel     <- sub('"$', "", sub('^load\\(\\s*"', "", .hits[1]))
  export_path <- normalizePath(file.path(dirname(ms_qmd), .ms_rel), mustWork = FALSE)
  rm(.ms_src, .pat, .hits, .ms_rel)
}
stopifnot(file.exists(export_path))
load(export_path)

# The SAME provisional 2026-07 cluster-label override that Manuscript_v5.3_2026-07-31.qmd
# and Appendix_v5.1_2026-07-31.qmd both source, applied here so the deck's cluster names
# match the paper's rather than the superseded trial-76 English names baked into the export.
# `chdir = TRUE` is required: the script's own internal CSV read is relative to the
# Manuscript folder, not to this deck's folder.
source("../../Cho-IIS/Manuscript/_cluster_labels_override.R", chdir = TRUE)

# --- accessor helpers, ported verbatim from Manuscript_v5.3_2026-07-31.qmd's Setup chunk,
# plus inv_row/j4cov from Appendix_v5.1_2026-07-31.qmd's Setup chunk (spec S3) -------------
model_stat <- function(model, field) model_fit_stats[[field]][match(model, model_fit_stats$model)]
coef_row <- function(term) path_b_table %>% filter(.data$term == !!term) %>% slice(1)
coef_row_bosc <- function(term) path_b_bosc_table %>% filter(.data$term == !!term) %>% slice(1)
fmt_est <- function(x, digits = 3) sprintf(paste0("%.", digits, "f"), x)
fmt_p <- function(p) {
  if (p < .001) return("< .001")
  paste0("= ", sub("^0", "", sprintf("%.3f", p)))
}
fmt_pv <- function(p) if (p < .001) "< .001" else sub("^0", "", sprintf("%.3f", p))
fmt_nz <- function(x, digits = 3) {
  s <- sprintf(paste0("%.", digits, "f"), x)
  sub("^(-?)0\\.", "\\1.", s)
}
fmt_nz_signed <- function(x, digits = 3) {
  s <- sprintf(paste0("%+.", digits, "f"), x)
  sub("^([+-])0\\.", "\\1.", s)
}
fmt_ci_nz <- function(lo, hi, digits = 3) {
  paste0("[", fmt_nz(lo, digits), ", ", fmt_nz(hi, digits), "]")
}
fmt_ci <- function(lo, hi, digits = 3) sprintf(paste0("[%.", digits, "f, %.", digits, "f]"), lo, hi)

rq2_row <- function(med, mod) {
  rq2_verdict_table %>% filter(.data$mediator == med, .data$moderator == mod) %>% slice(1)
}
h1_row <- function(out) h1a_h1b_omnibus %>% filter(.data$outcome == out) %>% slice(1)
h1_coef <- function(out, cl) {
  h1_cluster_coefficients %>%
    filter(.data$outcome == out, .data$term == paste0("cluster", cl)) %>% slice(1)
}
fm_row <- function(fct, cl) {
  h1_facet_map %>% filter(.data$facet == fct, .data$cluster == cl) %>% slice(1)
}
rq2_term <- function(med, mod, cl) {
  rq2_coefficient_slope_comparison %>%
    filter(.data$mediator == med, .data$moderator == mod, .data$cluster == cl) %>% slice(1)
}
bpath <- function(med, out) {
  h3ab_bpath_table %>% filter(.data$mediator == med, .data$outcome == out) %>% slice(1)
}
h3c_row <- function(med) {
  h3c_tie_type_table %>%
    filter(.data$mediator == med, str_detect(.data$quantity, "^b-path")) %>% slice(1)
}
ie_row <- function(out, cl) {
  h3_distrust_indirect_table %>% filter(.data$outcome == out, .data$cluster == cl) %>% slice(1)
}
n_sig_int    <- sum(rq2_coefficient_slope_comparison$b_p < .05, na.rm = TRUE)
n_corrob_w   <- sum(rq2_coefficient_slope_comparison$slope_corroborated_weighted, na.rm = TRUE)
n_corrob_d   <- sum(rq2_coefficient_slope_comparison$slope_corroborated, na.rm = TRUE)
n_interp     <- sum(rq2_coefficient_slope_comparison$interpretable_as_moderation, na.rm = TRUE)
n_gate_open  <- sum(!rq2_verdict_table$omnibus_null)
n_gate_shut  <- sum(rq2_verdict_table$omnibus_null)
n_design_agree <- sum(rq2_verdict_table$design_concordant)
gate_open_cells <- rq2_verdict_table %>%
  filter(!omnibus_null) %>%
  transmute(lbl = paste0(mediator, " × ",
                         ifelse(moderator == "N3_z", "security values", "distress"))) %>%
  pull(lbl) %>%
  paste(collapse = "; ")
mdc <- measurement_distinction_corr$long
r_of <- function(a, b) {
  mdc$r[(mdc$row == a & mdc$col == b) | (mdc$row == b & mdc$col == a)][1]
}
inv_row <- function(cmp) invariance_differences %>% filter(.data$comparison == cmp) %>% slice(1)
j4cov <- j4_construction_validation$channel_coverage

# Facet -> display label, keyed BY NAME. The slide table selects and renames through this
# vector, so a change in factor order can never silently re-label a column (it previously
# could: `kable(col.names = ...)` assigns positionally, and three of six columns were wrong).
facet_labels <- c(
  Aggression_online = "Online Aggr.",
  Disinfo_ops       = "Disinfo Ops",
  J4_distrust       = "Media Distrust",
  TV_threat         = "TV Threat",
  xMedia_FakeNews   = "xMedia Fake"
)

# Cluster 3's threat-side coefficients against the reference repertoire.
# NB: cluster 3 is *elevated on all four* threat facets, but it is NOT the highest on all
# four — cluster 6 is higher on TV_threat and xMedia_FakeNews. See VERIFY-LEDGER.md,
# NEEDS MJ #1: Manuscript v5.3 p.13 still carries the stronger "highest on all four"
# wording, which its own Table 2 contradicts. This deck states the defensible version.
cl3_threat_p_max <- max(
  h1_cluster_coefficients$p.value[
    h1_cluster_coefficients$term == "cluster3" &
      h1_cluster_coefficients$outcome != "J4_distrust"
  ]
)
```

```{r}
#| label: provenance
#| echo: false
#| results: asis
cat(sprintf(
  "<!-- IIS deck data provenance -- export: %s | manuscript: Manuscript_v5.3_2026-07-31.qmd | appendix: Appendix_v5.1_2026-07-31.qmd | cluster labels: provisional 2026-07-31 override, pending adjudication -->\n",
  export_path
))
```

```{r}
#| label: title-bg
#| echo: false
#| results: asis
#| warning: false

# --- Dynamic title background -------------------------------------------
# Leave NULL for a random pick; set to a filename in ../BG to override.
bg_choice <- NULL          # e.g. "sunset_grid.png"

bg_dir   <- "../BG"
bg_files <- list.files(bg_dir, pattern = "\\.(png|jpe?g|gif|webp)$",
                       ignore.case = TRUE, full.names = TRUE)

if (length(bg_files) > 0) {
  pick <- if (is.null(bg_choice)) {
    bg_files[sample.int(length(bg_files), 1)]   # random
  } else {
    file.path(bg_dir, bg_choice)                # override
  }

  if (file.exists(pick)) {
    uri <- xfun::base64_uri(pick)   # -> "data:image/png;base64,...."
    cat(paste0(
      '<script>(function(){',
      'var u="', uri, '";',
      'function apply(){',
        'var t=document.getElementById("title-slide");',
        'if(!t)return false;',
        't.setAttribute("data-background-image",u);',
        't.setAttribute("data-background-size","cover");',
        't.setAttribute("data-background-position","center");',
        't.setAttribute("data-background-opacity","0.1");',
        'if(window.Reveal&&Reveal.sync)Reveal.sync();',
        'return true;};',
      'if(window.Reveal&&Reveal.isReady&&Reveal.isReady()){apply();}',
      'else{document.addEventListener("DOMContentLoaded",function(){',
        'var n=0,iv=setInterval(function(){',
          'if((window.Reveal&&Reveal.isReady&&Reveal.isReady()&&apply())||++n>100)',
          'clearInterval(iv);},50);});}',
      '})();</script>'
    ))
  }
}
```

# The Puzzle

---

## Roadmap

1. **The one-construct assumption** — why treating informational insecurity as a single thing fails
2. **Fifteen media repertoires** — discovered by clustering, named by an LLM labeling agent
3. **What each facet does downstream** — differentiation, moderation, and two divergent effects on social capital
4. **What this buys communication theory** — a mechanism that is not singular

[Informational insecurity has (at least) two facets, and only one of them erodes connectedness.]{.neon-cyan}

::: notes
1. [⏱ 0:30]
2. 我會用四個部分來發展一個核心論點。
3. 首先，把 informational insecurity 當成單一 construct 為什麼行不通。
4. 第二，十五個媒體 repertoires，如何被發現、如何被命名。
5. 第三，每個 facet 在下游分別做了什麼。
6. 最後，這對傳播理論帶來什麼貢獻。
:::

---

## A Fragmented Media System — and a Hard Case

Fragmented, hybrid media systems mean **parallel informational ecosystems, not one shared environment** — ideological division, algorithmic filtering, contested credibility of outlets and gatekeepers.

**Taiwan is a hard case:** informational threat narratives, documented outlet-level ownership and self-censorship pressures, and low baseline trust in TV news.

[Audiences navigate parallel informational ecosystems, not one shared environment.]{.neon-cyan}

[Bennett & Livingston (2018); Chadwick (2017); Skrzypczak (2019); Chang & Tang (2023).]{.citation}

::: notes
1. [⏱ 0:35]
2. 破碎化、混合式的媒體系統，改變了人們理解風險與歸屬的方式。閱聽人面對的是平行的資訊生態系，不是單一共享環境。
3. 台灣是一個特別困難的案例：兩岸資訊壓力、媒體所有權與自我審查的紀錄，以及電視新聞信任基準偏低（Chang & Tang 2023 記錄到只有大約 46–47% 的人信任電視新聞）。
4. 這是整場演講的經驗場景設定——講快一點，重點在下一張的概念轉折。
:::

---

## One Construct, or Two?

:::: {.columns}
::: {.column width="50%"}
#### Perceived informational threat

Media content is manipulative, hostile, sensational, or false.
:::
::: {.column width="50%"}
#### Media distrust

Low assessed credibility of the outlets that make up the media system.
:::
::::

::: {.theory-box}
**M1:** separability is a **measurement premise**, not a hypothesis under test — the media-trust literature has no agreed operationalization, and audiences parse the construct multiply.
:::

[The two facets are stated as separable by premise, not proven separable as a finding.]{.neon-cyan}

[Strömbäck et al. (2020); Knudsen et al. (2021).]{.citation}

::: notes
1. [⏱ 1:00]
2. 這是整場演講的概念轉折點。
3. Perceived informational threat 關心的是內容本身；media distrust 關心的是對媒體機構可信度的整體評估。
4. M1 是一個 measurement premise，不是待檢驗的 hypothesis——媒體信任文獻本身就沒有共同的操作型定義，一般民眾對這個構念的理解也是多元的。
5. 後面 RQ1 的結果，會是這個 premise 的經驗內容，而不是對它的檢驗。
:::

---

## IIS: The Framework and What It Predicts

```{r}
#| label: tbl-hyp-grid
tibble::tribble(
  ~RQ, ~Hypotheses, ~Content,
  "RQ1", "H1a, H1b", "Repertoires differentiate perceived threat and, separately, media distrust.",
  "RQ2", "H2a / H2b / H2c", "No moderation / amplification / attenuation of repertoire -> threat by distress or security values.",
  "RQ3", "H3a / H3b / H3c", "Erosion vs. compensation of social capital; H3c is a magnitude claim about tie-type strength."
) %>%
  knitr::kable()
```

::: {.theory-box}
H2b and H2c are alternatives *within* a cell but **not mutually exclusive across repertoires** — amplification in one, attenuation in another, is a patterned outcome, not a contradiction.
:::

[The framework states competing predictions ex ante and adjudicates each per facet.]{.neon-cyan}

::: notes
1. [⏱ 0:55]
2. RQ1 問repertoires 是否讓兩個 facet 出現不同的分化型態。
3. RQ2 把 H2a/H2b/H2c 設定成三分結構：不調節、放大、或減弱。
4. RQ3 把 erosion 與 compensation 設為對立假設，並加入 H3c 這個關於「強度」而非「方向」的主張。
5. 重點是：H2b 與 H2c 在同一個 cell 內互斥，但跨 repertoire 並不互斥——兩者同時出現是結果，不是矛盾。
6. 下一張把這些對立說成人話——不要在這裡就講完。
:::

---

## What's Actually at Stake {.smaller-content}

:::: {.columns}
::: {.column width="56%"}
#### Amplification (H2b) vs attenuation (H2c)

Does an existing vulnerability make the same media diet **hit harder**, or **stop mattering**?

- *Amplify* — the same film is scarier if you are already jumpy.
- *Attenuate* — the twenty-year loyal viewer: feeling worse changes nothing, because for them distress and diet have come apart.

#### Erosion (H3a) vs compensation (H3b)

Same starting point, opposite bets on what people do next.

- *Erode* — you stop extending the benefit of the doubt past people you already know.
- *Compensate* — media hostility sends you **looking** for people to check things against.
:::
::: {.column width="44%"}
::: {.theory-box}
**Bonding** ties are the people who would help you move house at 2 a.m. — family, close friends.

**Bridging** ties are the people who would tell you about a job in a field you don't work in — acquaintances, neighbours, colleagues from another floor.

Bridging is where cross-cutting information and perspective come from; bonding is where support comes from.
:::

Both sides of each pair are documented in the literature. That is why they are stated as rivals and **adjudicated**, not assumed.
:::
::::

[A society that keeps only bonding is one where everyone has support and nobody has common ground.]{.neon-cyan}

::: notes
1. [⏱ 1:15]
2. 這張是為了讓 hypotheses 變成「活的」——不是為了補充定義。
3. **Amplification（H2b）**：兩個人看同一則晚間新聞，本來就焦慮、睡不好的那一個，看完更確信媒體在誤導他。同樣的 diet，效果更強——就像你本來就緊張的時候，同一部片會更可怕。
4. **Attenuation（H2c）**：二十年只看同一台的忠實觀眾。他心情變差，並不會讓那則播報打得更重，因為對他來說 distress 和 media diet 早就脫鉤了。Cultivation theory 自己就預測過這種情況：當一個結果已經飽和，斜率本來就會變平。
5. **Erosion（H3a）**：如果你認為整個新聞系統在騙你，你就不會再把「善意推定」延伸到你認識的人以外。隔壁貼著另一個政黨貼紙的鄰居，變成一個你什麼都不跟他討論的人。
6. **Compensation（H3b）**：相反的賭注——媒體的敵意反而把你推出去找人查證。你在飯桌上爭論、你加入 LINE 群組、你出現在社區會議。
7. **Bridging / bonding 一定要在這裡講清楚**，因為 RQ3 完全建立在這個區分上，而聽眾多半不熟這兩個詞。Bonding 是凌晨兩點會來幫你搬家的人；bridging 是會告訴你另一個行業有職缺的人。
8. 收尾這一句要慢——「一個只剩 bonding 的社會，是每個人都有人支持、卻沒有人有共同基礎的社會。」這就是 RQ3 為什麼重要。
:::

# Finding and Naming Media Repertoires

---

## Data and the Sample Funnel

Taiwan Communication Survey, nationally representative, stratified multi-stage PPS. Pooled 2022 + 2024 outcome sample, wave weights normalized to within-wave mean 1, `Year` fixed effect. The 2023 wave enters the typology only — it carries no threat battery.

::: {.stat-card}
**`r format(n_clustered, big.mark = ",")`** 3-wave typology sample

**`r format(n_outcome, big.mark = ",")`** outcome sample (2022+2024; 2,015 + 2,016)

**`r format(n_analytic, big.mark = ",")`** analytic (noise cluster dropped)

**`r format(n_modeled, big.mark = ",")`** modeled (complete-case)

**`r format(n_j4_analytic, big.mark = ",")`** distrust-model analytic (*n*<sub>J4</sub>)
:::

[The funnel narrows for different reasons at each step, not by attrition alone.]{.neon-cyan}

::: notes
1. [⏱ 0:50]
2. TCS 是全國代表性的多階段 PPS 抽樣調查。
3. 三波合併的分群樣本用於建立 typology；2022+2024 的結果樣本用於後續模型。
4. 每個波的權重先做 within-wave 常態化，再合併，並加入 Year 固定效果。
5. 2023 只用於 typology，因為它沒有 threat battery、社會資本模組或 distress 題組。
:::

---

## Discovering Repertoires: UMAP + HDBSCAN + Optuna

Binary indicators of frequent use across 100+ news sources (TV, online, hybrid) → UMAP → HDBSCAN, Optuna-tuned. **Trial 76** selected on DBCV, the primary criterion for density-based solutions, with noise ratio, silhouette, Calinski–Harabasz and Davies–Bouldin as secondary comparisons.

:::: {.columns}
::: {.column width="55%"}
- relational configurations of **co-used sources**, not summed exposure volume
- why *repertoire*, not *media diet*
- Trial 76 sits at the high-DBCV frontier with a balanced cluster-size distribution
:::
::: {.column width="45%"}
```{r}
#| label: fig-cluster-metrics-slide
#| fig-width: 5
#| fig-height: 4.2
fig_cluster_metrics_obj + theme_sw()
```
:::
::::

[Repertoires are relational configurations of co-used sources, not summed exposure volume.]{.neon-cyan}

::: notes
1. [⏱ 1:00]
2. 分群的輸入是 100 多個新聞來源的二元使用指標。
3. UMAP 降維、HDBSCAN 分群，超參數由 Optuna 調校，Trial 76 在 DBCV 上被選為最終解。
4. Silhouette 在整個 trial 空間中變化幅度很窄，區辨力較弱，所以只作為輔助指標，不與 DBCV 並列成同一件事。
5. 核心論點：repertoire 是共同使用來源的關係型配置，不是加總的暴露量——這也是為什麼用 repertoire 而不是 media diet。
:::

---

## Naming Them: LLM Structured Labeling {.tight}

**What the ranking measure is.** Added value is a **difference**, not a ratio: $AV = m_c - m_t$ — an outlet's prevalence *within* the cluster minus its prevalence in the reference population (all clustered respondents, noise cluster excluded). No prevalence floor, no significance filter. Panels hold the top twenty at positive AV, so **panel length varies with how many outlets a cluster genuinely over-uses — a thin panel is a result, not a failure.**

:::: {.columns}
::: {.column width="52%"}
#### Why a difference, not lift

Lift **saturates**: an outlet used *only* by cluster members hits the maximum $1/P(\text{cluster})$ whether three people use it or five hundred. A difference cannot — $AV$ is bounded above by $m_c$, so a handful of users cannot climb the table however exclusive they look. **That bound is why no prevalence floor is needed:** the rare tail is handled structurally, not by a threshold someone picked.

#### The cost, stated honestly

A difference over-weights the **common** tail exactly as lift over-weights the rare one. So a cluster that simply uses more outlets posts big gaps for that reason alone. The fix is not in the sort key — **each cluster's header carries its repertoire size**, and the labeler was told to read gaps against it.
:::
::: {.column width="48%"}
#### What the model actually receives — four things

1. a **header line** — cluster size, mean online outlets vs the population mean;
2. a **positive panel** — over-used outlets, with summary statistics and item type;
3. a short **negative panel** — most under-used outlets, for avoidance-based reasoning only;
4. **media-format metadata**.

Columns are $n_c$, $m_c$, $m_t$ — and **lift as a labelled context column only**, carrying a standing note that it is unreliable at low $n$ and must never drive the sort.

`gpt-5.6-sol`, structured JSON → **30 independent replicates**, agreement measured; adjudication pending.
:::
::::

::: {.theory-box}
Inter-coder reliability is the standard for *supervised* coding and a category mismatch for *unsupervised* discovery — the burden shifts to post-hoc validation: **semantic**, **replicate agreement**, **predictive**. · One wrinkle disclosed to the model: of the 120 binary indicators, `vb7` is a one-hot expansion of a **single-choice** item, so its levels are mutually exclusive — a `vb7` row reports **modal choice, not breadth**.
:::

[The labeling schema carries no ideological-orientation field, and no claim here rests on a model-assigned political leaning.]{.neon-cyan}

[Hahsler (2015); Brin et al. (1997); Tan et al. (2004); Song et al. (2016); Lavrač et al. (1999); Monroe et al. (2008); DiMaggio et al. (2013); Grimmer & Stewart (2013); Pham et al. (2024).]{.citation}

::: notes
1. [⏱ 1:40]
2. 這張投影片是本研究在**測量**上的貢獻，不只是「我們用了 LLM」。重點在於：標籤模型只看得到分析者放在它面前的特徵，所以**挑選特徵的統計量決定了標籤能講什麼**。
3. **Added value 是差值不是比值**：$AV = m_c - m_t$。參照母體是所有分群的受訪者、排除 noise cluster（N = 6,102；noise cluster 只有 4 人）。沒有 prevalence floor，沒有顯著性篩選。
4. **為什麼是差值——關鍵是有界性。** 只有某個 cluster 的人用的媒體，lift 會直接衝到最大值 $1/P(\text{cluster})$，不管用的人是三個還是五百個。差值不會這樣飽和：AV 的上界就是 $m_c$，所以一個 532 人 cluster 裡只有三個人用的媒體，AV 不可能超過 **0.0056**，再怎麼「專屬」也爬不上表。**這個上界本身就取代了 prevalence floor** ——不是靠某人挑的門檻。
5. 文獻脈絡（appendix S2.1）：比值型的 distinctiveness 在低頻時不穩定（Hahsler；Brin；Tan et al.），而 subgroup discovery 要求 deviation factor 搭配 size factor（Song；Lavrač）。在單一 cluster 之內，用 AV 排序等同於用 weighted relative accuracy 排序，也就等同於 novelty。
6. **代價要誠實講**：差值會過度偏重**常見**的尾巴，就像 lift 過度偏重稀有的尾巴（Monroe et al.）。這裡確實成立——120 個特徵裡最高的母體使用率是 40.6%。所以只是「用得比較多」的 cluster，光靠這一點就會在熱門媒體上拉出大 gap。
7. 解法不在排序鍵，而在**呈現**：每個 cluster 的 header 都帶著它的 repertoire size（成員平均使用的線上媒體數，對比母體平均 4.46），而且明確告訴標籤模型：**在高母體使用率上的小 gap 不是 distinctiveness，不管它排多高。**
8. 模型收到的是**四樣東西**，不是一張表：header line、positive panel、簡短的 negative panel（有兩個 cluster 部分是由它們「不用什麼」定義的）、以及 media-format metadata。lift 有出現，但只作為標示清楚的脈絡欄位，附帶「低 n 時不可靠、絕不可用來排序」的常設註記。
9. **vb7 的細節**（如果有人問）：120 個二元指標分成六個 block，其中 vb7 有 50 個 level，但它**不是**多選的品牌題組——它是單選題「您最常看哪一台電視新聞？」的 one-hot 展開，加上一個「不看電視新聞」的 level。各 level 互斥，95.1% 的受訪者剛好落在一個。所以 vb7 那一列講的是**最常選擇**，不是**廣度**；當好幾個互斥頻道都出現中等數值時，**那個分散的型態本身就是發現**，而不是任何單一頻道的弱證據。
10. **複本一致性（appendix S2.1，Table 8）**：兩個數字必須一起讀。15 個 cluster 裡有 14 個達到 **100% 語意群組一致**，但**逐字一致只有 3.3% 到 30.0%**。Cluster 11 是極端案例：30 次跑出 30 個不同的字串，卻全部被歸為同一個語意群組。只報語意那個數字，等於讓「100% 一致」這個宣稱完全靠一個沒說出口的門檻撐著。誠實的講法也是比較強的講法：**用字的變異很大，底下的理解很穩定——除了 cluster 11，那裡用字的變異是全面的。**
11. 標籤的可信度不靠模型自報的 confidence（那只是描述性的），而靠三項檢驗：語意效度、複本一致性、預測效度。
12. **這些標籤目前是暫定的（provisional）**，30 次複本的裁決仍在進行中。
:::

---

## Fifteen Repertoires {.smaller-content}

```{r}
#| label: fig-cluster-media-slide
#| fig-width: 11
#| fig-height: 5
fig_cluster_media_obj + theme_sw()
```

[Fifteen distinct usage profiles, not fifteen shades of the same profile.]{.neon-cyan}

[Cluster 0 (`r clab(0)`) is the reference; the noise cluster is dropped. `r cluster_labels_provisional_note`]{.citation}

::: notes
1. [⏱ 0:40]
2. 這張圖呈現十五個 repertoire 在六類媒體來源群組上的使用率。
3. Cluster 0 是建模參照組，noise cluster 已被排除。
4. 完整的十五列命名表在 backup B1，這裡先看整體形態。
5. 提醒：標籤仍是暫定版本。
:::

---

## Measuring Both Facets {.smaller-content}

**Perceived threat.** JB1/JB2 batteries, 18 dichotomous items; EFA (ML, tetrachoric, oblimin) → four factors. **Mediators are ten-Berge factor scores, not unit-weighted sums.** Names (Aggression online, Disinfo ops, TV threat, xMedia FakeNews) are interpretive labels. $\alpha$ = `r sprintf("%.2f", min(mediator_reliability_table$alpha))`–`r sprintf("%.2f", max(mediator_reliability_table$alpha))`.

**Media distrust.** J4, 0–100 credibility per channel, five channels, reversed, mean over **available** channels — per-channel by design, since the referent determines what a trust study finds.

**Moderators and outcomes.** Distress (harmonized four constructs, $\alpha$ = `r sprintf("%.3f", distress_reliability)`, metric invariance holds); security values (N3); BSC/BoSC from Williams' ISCS ($\alpha$ = `r sprintf("%.2f", bsc_reliability)`, `r sprintf("%.2f", bosc_reliability)`).

[The four threat names are interpretive labels for oblique factors, not definitions of scales.]{.neon-cyan}

::: notes
1. [⏱ 0:50]
2. 威脅知覺來自 JB1/JB2 兩組多選題，共 18 個二元題目，EFA 抽出四個因素。
3. Mediator 是 ten-Berge factor scores，不是題目加總——這是為了保留四個 facet 之間本來就存在的相關。
4. 媒體不信任用 J4，逐頻道詢問可信度後反向計分，取可得頻道的平均，因為信任研究的結果高度依賴問的是哪個對象。
5. Distress 通過了 metric invariance 檢定；BSC/BoSC 來自 Williams 的 ISCS 量表。
:::

---

## How a Claim Gets Made Here {.smaller-content}

**Estimators.** Weighted `lm` primary; stratified `svyglm` design-based robustness check.

::: {.theory-box}
**Neither is unambiguously conservative** — `lm(weights=)` treats weights as precision weights (anti-conservative SEs); the pooled design is strata-only because the PSU identifier is absent from the 2022 release (design-based SEs are themselves a lower bound).
:::

**The interpretability criterion — a term is read only if *both* gates open.**

:::: {.columns}
::: {.column width="50%"}
**(i) Omnibus gate** — 14-df *F* on the full interaction block, before any term inside it is read.

*Plainly:* before asking whether any **one** repertoire behaves differently, ask whether the fifteen differ from each other **at all, as a set**. If the set shows nothing, one repertoire looking different is very likely the product of having looked fifteen times.

> Flip fifteen coins. One coming up heads eight times in ten hasn't found you a biased coin — it has found you fifteen coins.
:::
::: {.column width="50%"}
**(ii) Reference-free corroboration** — the repertoire's own simple slope at ±1 SD via `emmeans`.

*Plainly:* an interaction coefficient answers a **comparison** question — does distress matter *more* here than in cluster 0? It never says distress matters here *at all*. So we ask, for that group alone: at high distress versus low, does perceived threat actually differ?

> "Taipei is warmer than Yilan today" does not tell you whether Taipei is warm.
:::
::::

**The nulls are informative, not indeterminate:** the design detects $f^2 \ge$ `r sprintf("%.4f", max(rq2_power_table$min_detectable_f2))` at 80% power, so **a closed gate rules out moderation of ordinary size.**

[The gate protects interpretation; it is not a familywise correction, so repertoire-level patterns are labelled descriptively.]{.neon-cyan}

::: notes
1. [⏱ 1:30]
2. 這張投影片決定了後面所有結果怎麼被讀——講慢一點，這裡投資的時間，後面三個 RQ 都會回收。
3. 兩種估計法都不是天然保守的，所以兩者並列報告，而不是挑一個當作嚴格標準。
4. **Omnibus gate 的白話版**：先問「這十五個 repertoire 作為一個集合，彼此之間到底有沒有差異」，再問「哪一個不一樣」。如果整個集合看不出東西，那單獨一個看起來不一樣的，多半是因為你看了十五次。
   - 硬幣的比喻要講出來：丟十五枚硬幣，其中一枚十次裡有八次正面——你沒有找到一枚有偏的硬幣，你只是找到了十五枚硬幣。
5. **Reference-free corroboration 的白話版**：交互作用係數回答的是**比較**問題——distress 在這一群裡是不是比參照組（cluster 0）更重要？它**沒有**說 distress 在這一群裡重不重要。一個群體可以跟參照組有差異，自己的斜率卻是平的——只要參照組的斜率往反方向跑就會這樣。所以我們回頭單獨問這一群：高 distress 對比低 distress，perceived threat 真的有差嗎？這就是 simple slope，而且它不依賴我們剛好把誰設為參照組。
   - 天氣的比喻：「今天台北比宜蘭暖」並沒有告訴你台北暖不暖。
6. 兩者都滿足，才算 interpretable as moderation——這不是 familywise correction，所以每個 repertoire 的型態仍用描述性語氣呈現。
7. **最後一句很重要**：這個設計在 80% power 下可以偵測到 f² `r sprintf("%.4f", max(rq2_power_table$min_detectable_f2))` 以上的效果，遠低於慣例的小效果標準。所以 gate 關閉不是「我們什麼都沒找到」，而是「一般大小的調節效果被排除了」。沒有這一句，整個 RQ2 段落聽起來會像是一無所獲。
:::

# What the Repertoires Do

---

## RQ1: Both Facets Differentiate

The 14-df repertoire block is significant for all five outcomes, under both estimators. Threat-facet block *F* range `r sprintf("%.2f", min(h1a_h1b_omnibus$F_weighted[h1a_h1b_omnibus$hypothesis == "H1a (perceived threat)"]))`–`r sprintf("%.2f", max(h1a_h1b_omnibus$F_weighted[h1a_h1b_omnibus$hypothesis == "H1a (perceived threat)"]))`, all *p* `r fmt_p(max(h1a_h1b_omnibus$p_weighted[h1a_h1b_omnibus$hypothesis == "H1a (perceived threat)"]))`; media distrust *F* `r sprintf("%.2f", h1_row("J4_distrust")$F_weighted)`, *p* `r fmt_p(h1_row("J4_distrust")$p_weighted)`.

Effect sizes are small — Cohen's $f^2$ `r sprintf("%.3f", min(h1a_h1b_omnibus$f2_weighted))`–`r sprintf("%.3f", max(h1a_h1b_omnibus$f2_weighted))` — what a fifteen-category contrast on a large national sample should yield.

[H1a and H1b are both supported, under both estimators.]{.neon-cyan}

::: notes
1. [⏱ 0:40]
2. 14 df 的 repertoire block 在五個結果變項上都顯著，兩種估計法皆然。
3. 效果量偏小，這正是十五類對比在大型全國樣本下應有的樣貌，不代表結果不重要。
4. H1a、H1b 都成立，這是後面所有分析的起點。
:::

---

## RQ1: But Not in the Same Order {.tight}

```{r}
#| label: tbl-h1-facet-map-slide
h1_facet_map %>%
  mutate(cell = sprintf("%+.2f", weighted_mean)) %>%
  select(facet, repertoire, cell) %>%
  pivot_wider(names_from = facet, values_from = cell) %>%
  arrange(as.integer(str_extract(repertoire, "^[0-9]+"))) %>%
  # Name-keyed, like the manuscript's gt()/cols_label(): all_of() errors loudly if a facet
  # is missing, and the labels travel with their column rather than with a position.
  select(Repertoire = repertoire, all_of(names(facet_labels))) %>%
  rename_with(~ facet_labels[.x], .cols = all_of(names(facet_labels))) %>%
  knitr::kable()
```

Cluster 3 (`r clab(3)`) is **elevated on all four threat facets** against the reference (largest *p* `r fmt_p(cl3_threat_p_max)`), top-ranked on both online facets — and sits at rank `r fm_row("J4_distrust", 3)$rank` of 15 in distrust.

[Two facets a one-dimensional media-cynicism account would place together sit at opposite ends — the empirical content of M1.]{.neon-cyan}

::: notes
1. [⏱ 1:00]
2. 這是 RQ1 的核心投影片。
3. Cluster 3（`r clab(3)`）在四個威脅 facet 上都顯著高於參照組（最大的 *p* `r fmt_p(cl3_threat_p_max)`），兩個 online facet 更是排名第一；但在 media distrust 上卻排在第 `r fm_row("J4_distrust", 3)$rank` 名（共 15 名）。
   - 注意用字：是「四個 facet 都偏高」，**不是**「四個 facet 都最高」——TV threat 與 xMedia fake 的最高者是 cluster 6（`r clab(6)`）。論文 v5.3 第 13 頁目前寫的是較強的說法，與它自己的 Table 2 不一致（見 VERIFY-LEDGER.md）。
4. 這個反轉正是 M1 的經驗內容：如果兩個 facet 是同一個潛在構念，不應該出現這種分離。
5. 兩個關於這個排序的解讀都是 post-hoc：partisan 解讀與 engagement-detachment 解讀。partisan 解讀不成立——cluster 0（`r clab(0)`），這個 facet 上最大、且建立在明確親藍頻道之上的 repertoire，distrust 排名居中偏低（第 `r fm_row("J4_distrust", 0)$rank` 名），不在應有的高 distrust 端；Blue/Green 二分並不能組織這個排序，我們選擇報告這個「失敗」而不是略過。Engagement-detachment 解讀描述上表現較好，但也是 post-hoc。
:::

---

## RQ2: From Significant Terms to Interpretable Moderation

`r n_sig_int` significant interaction terms → `r n_corrob_w` corroborated (weighted) / `r n_corrob_d` (design-based) → **`r n_interp`** interpretable. `r n_corrob_w - n_interp` corroborated terms sit in cells whose omnibus block is null — a corroborated slope does not re-open a gate that never opened.

`r n_gate_open` of ten cells open the gate (`r gate_open_cells`); `r n_design_agree` of ten agree under design-based inference.

[That chain governs every moderation claim in this study.]{.neon-cyan}

::: notes
1. [⏱ 1:00]
2. 從 `r n_sig_int` 個顯著交互作用項開始，只有 `r n_corrob_w` 個在加權估計下通過 reference-free 的 simple-slope 檢驗。
3. 同時滿足 gate 開啟與 corroboration 兩個條件的，只剩 `r n_interp` 個——這條鏈決定了整篇論文所有的 moderation 主張。
4. 十個 cell 中有 `r n_gate_open` 個 gate 是開的，design-based 估計在其中 `r n_design_agree` 個上一致。
:::

---

## RQ2: Amplification *and* Attenuation

```{r}
#| label: tbl-rq2-interpretable-slide
rq2_coefficient_slope_comparison %>%
  filter(interpretable_as_moderation) %>%
  transmute(
    Cell = paste0(mediator, " × ", ifelse(moderator == "N3_z", "Security", "Distress")),
    Repertoire = repertoire,
    `Interaction b` = sprintf("%+.3f", b_interaction),
    Direction = b_direction,
    `Simple slope` = sprintf("%+.3f", slope_lm),
    `Design-robust` = ifelse(slope_corroborated, "yes", "no")
  ) %>%
  knitr::kable()
```

The two SET TV rows are **primary-estimator-only** — see the `Design-robust` column.

::: {.theory-box}
Attenuation is conditional cultivation's own boundary-condition case — cultivation was specified to flatten under ceiling effects and to moderate selectively within studies.
:::

[Amplification and attenuation coexist across repertoires — the result, not an inconsistency.]{.neon-cyan}

[Hetsroni (2014); Russell & Buhrau (2015).]{.citation}

::: notes
1. [⏱ 0:40]
2. 兩個放大：`r clab(10)` 的安全價值 × online aggression，以及 `r clab(14)` 的 distress × TV threat，兩者都 design-robust。
3. 一個減弱：`r clab(2)` 的 distress 同時減弱 disinformation 與 online aggression 的關聯，但**只在加權估計下**通過 corroboration——design-based 的 simple-slope *p* 分別是 `r fmt_pv(rq2_term("Disinfo_ops", "Distress", 2)$slope_svy_p)` 與 `r fmt_pv(rq2_term("Aggression_online", "Distress", 2)$slope_svy_p)`。這個但書在論文裡每次用到 attenuation 結果時都會重述，被問到就直接講這兩個數字。
4. 這不是反常，而是 conditional cultivation 理論自己允許的邊界條件——當某個結果變項接近天花板效應時，涵化效果本來就該減弱。
:::

---

## RQ2: The Moderator's Own Effect Is Itself a Result {.smaller-content}

**In a model with fifteen repertoires and their interactions, the coefficient labelled "distress" is not the effect of distress.** It is the effect of distress **inside cluster 0** — the reference group is the only one for which every interaction term is switched off. `W_overall_slope` averages all fifteen groups' own slopes: the quantity people *think* they are reading.

::: {.theory-box}
Reporting the bare coefficient as a general effect is reporting a national average from one city.
:::

**The demonstration.** For Disinfo_ops × Distress the *bare reference-repertoire* coefficient ($b$ `r fmt_est(rq2_row("Disinfo_ops", "Distress")$W_main_b)`, $p$ `r fmt_p(rq2_row("Disinfo_ops", "Distress")$W_main_p)`) is clearly significant, while the cluster-averaged slope straddles zero ($b$ `r fmt_est(rq2_row("Disinfo_ops", "Distress")$W_overall_slope)`, CI `r fmt_ci(rq2_row("Disinfo_ops", "Distress")$W_overall_slope_lo, rq2_row("Disinfo_ops", "Distress")$W_overall_slope_hi)`). Same model, same data, **two sentences that contradict each other — and only one of them is about Taiwanese adults.**

Read as overall slopes, security values raise perceived threat on three of four threat facets; distress does not, only TV threat reaching a comparable slope. Distress does raise the *level* of media distrust (`r fmt_est(rq2_row("J4_distrust", "Distress")$W_overall_slope)`) while the J4 × Distress interaction block is null — so the indirect effects below are treated as unmoderated.

[A moderator can shift the level of a facet without conditioning the repertoire pathway at all.]{.neon-cyan}

::: notes
1. [⏱ 1:05]
2. **先講清楚那個係數是什麼**：在一個有十五個 repertoire 和它們交互作用項的模型裡，標著「distress」的那個係數**不是 distress 的效果**。它是 distress **在 cluster 0 裡面**的效果——參照組是唯一一個所有交互作用項都被關掉的組別。如果 cluster 0 本身就不典型，那個數字就只在描述 cluster 0。
3. `W_overall_slope` 是十五個組別各自斜率的平均，也就是大家**以為**自己在讀的那個量。
4. 比喻：把裸係數當成一般效果來報告，等於拿一個城市的數字當全國平均。
5. **示範**：Disinfo_ops × Distress 的裸係數 `r fmt_est(rq2_row("Disinfo_ops", "Distress")$W_main_b)`（$p$ `r fmt_p(rq2_row("Disinfo_ops", "Distress")$W_main_p)`）明顯顯著，但跨群平均斜率是 `r fmt_est(rq2_row("Disinfo_ops", "Distress")$W_overall_slope)`，信賴區間跨過零。同一個模型、同一批資料，兩個互相矛盾的句子——而只有其中一句在講台灣成年人。
6. 注意用字：security values 在四個 threat facet 中的三個上提高了 perceived threat；**distress 則沒有——只有 TV threat 達到相當的斜率**。這個但書要講，論文裡有。
7. Distress 會提高 media distrust 的整體**水準**，但 J4 × Distress 的 block 是 null，所以它沒有改變 repertoire → distrust 這條路徑本身；後面的 indirect effect 都當作未被調節來處理。
8. **報告規則（給提問者，不是給投影片）**：一律報 `W_overall_slope`，不要報裸的 `W`。這是論文 Methods 明訂的。
:::

---

## RQ3: Distrust Erodes; Threat Does Not

```{r}
#| label: tbl-h3ab-bpath-slide
h3ab_bpath_table %>%
  transmute(
    Facet = ifelse(str_detect(pathway, "distrust"), "Media distrust", mediator),
    Outcome = outcome,
    `b (wtd)` = sprintf("%+.3f", estimate),
    `95% CI` = sprintf("[%+.3f, %+.3f]", conf.low, conf.high),
    `p (wtd / design)` = paste0(
      ifelse(p.value < .001, "<.001", sub("^0", "", sprintf("%.3f", p.value))), " / ",
      ifelse(p_design < .001, "<.001", sub("^0", "", sprintf("%.3f", p_design)))
    ),
    Status = design_status
  ) %>%
  knitr::kable()
```

**H3a supported, carried entirely by media distrust** (BSC design-robust; BoSC marginal under design-based inference). None of the four threat facets erodes either tie type.

[The headline is a divergence between facets, not a single verdict.]{.neon-cyan}

::: notes
1. [⏱ 1:00]
2. Media distrust 對兩種社會資本都是負向的：BSC 在 design-based 下依然穩健，BoSC 只是 marginal。
3. 四個威脅 facet 沒有一個會侵蝕任一種 tie type——有些甚至是正向的。
4. 這就是這篇論文的頭條發現：兩個 facet 在下游走向完全不同的方向。
:::

---

## RQ3 / H3c: Bridging Erodes Harder

$\Delta b$ is the difference between two slopes, **both of which are negative** — so this is a question about which falls faster, never about which rises.

$\Delta b$ = `r fmt_est(h3c_row("J4_distrust")$delta_b)`, 95% CI `r fmt_ci(h3c_row("J4_distrust")$delta_lo, h3c_row("J4_distrust")$delta_hi)`, excluding zero: bridging ties erode about **`r sprintf("%.1f", h3c_row("J4_distrust")$strength_ratio_BSC_over_BoSC)`×** more strongly than bonding. Supported for distrust and no threat facet — all four threat $\Delta b$ CIs contain zero.

::: {.theory-box}
**Two buckets, both leaking.** Bridging leaks about `r sprintf("%.1f", h3c_row("J4_distrust")$strength_ratio_BSC_over_BoSC)`× faster than bonding. At the end, proportionally more of what is left is bonding — **but there is less water. Nobody gained anything.**
:::

The nearest prior ordering (Beaudoin 2011: bonding β = .26 > bridging β = .17) runs the other way — a contribution, not a replication.

[Nothing here supports a claim that people "turn to" bonding ties when they distrust the media.]{.neon-cyan}

::: notes
1. [⏱ 1:00]
2. **先說 Δb 是什麼**：它是兩條斜率的差，而**兩條都是負的**。所以這個問題從頭到尾是「哪一個掉得比較快」，不是「哪一個上升」。這是全篇最容易被誤報的一件事。
3. Delta b = `r fmt_est(h3c_row("J4_distrust")$delta_b)`，95% CI `r fmt_ci(h3c_row("J4_distrust")$delta_lo, h3c_row("J4_distrust")$delta_hi)`，排除零；bridging 大約以 `r sprintf("%.1f", h3c_row("J4_distrust")$strength_ratio_BSC_over_BoSC)` 倍的強度比 bonding 侵蝕得更快。四個 threat facet 的 Δb 信賴區間全都含零。
4. **水桶的比喻要講出來，這是聽眾唯一會記得的東西**：兩個水桶都在漏。Bridging 漏的速度大約是 bonding 的 `r sprintf("%.1f", h3c_row("J4_distrust")$strength_ratio_BSC_over_BoSC)` 倍。到最後，剩下的水裡 bonding 的比例確實變高了——**但水變少了。沒有人得到任何東西。**
5. 這樣講，就不可能被聽成「人們轉向 bonding ties」。這是 compositional shift，不是 mobilization。
6. 這個方向跟最接近的前人研究（Beaudoin 2011：bonding β = .26 > bridging β = .17）相反，所以是一個 contribution，不是複製。構念不完全相同，所以不是直接矛盾。
:::

---

## RQ3 / H3b: Compensation Is the Weakest Claim

Two threat facets positively associated with connectedness under the primary estimator: TV threat → BSC and online aggression → BSC/BoSC. Only **TV threat → BSC** survives design-based inference (*p* `r fmt_p(bpath("TV_threat", "BSC")$p_design)`); both online-aggression paths go marginal.

::: {.theory-box}
**"Survives design-based inference" — plainly.** We estimated everything **two ways**, and *neither is the strict one*: the primary estimator probably draws its error bars too tight because it treats survey weights as precision weights; the design-based one probably does too, because the pooled design is missing its cluster identifier. When both agree we say so; when only one agrees we say that too, and we do not lean on it. **Compensation is the case where only one agrees.**
:::

External picture is mixed: Leong et al. (2023) positive but different domain; Neyazi et al. (2021) null; Goodwin et al. (2005) runs to bonding.

[Supported weakly and locally — a direction for future work, not a finding delivered.]{.neon-cyan}

::: notes
1. [⏱ 1:00]
2. 兩個威脅 facet 在主要估計法下與 connectedness 正相關：TV threat → BSC，以及 online aggression → BSC/BoSC。
3. 但只有 **TV threat → BSC** 在 design-based 檢驗下依然穩健（*p* `r fmt_p(bpath("TV_threat", "BSC")$p_design)`）；兩條 online aggression 的路徑都變成 marginal。
4. **「survives design-based inference」要翻成白話**，因為聽眾不會知道這句在做什麼工，而它其實承擔了全部的重量：
   - 我們把每件事都用**兩種方法**估計。
   - **兩種都不是那個「嚴格的」方法**。主要估計法可能把誤差棒畫得太窄，因為它把抽樣權重當成精確度權重；design-based 那個大概也太窄，因為合併後的設計缺了 PSU 識別碼。
   - 兩個都同意，我們就說兩個都同意；只有一個同意，我們也照實說，而且不倚賴它。
   - **Compensation 就是只有一個同意的那個案例。**
5. 外部文獻的證據也是混合的，不是一致支持的方向——所以這是「往哪裡走」的指示，不是一個已經交付的發現。
6. 這是全篇最脆弱的一個主張，講的時候不要幫它加碼。
:::

# What It Buys Us

---

## Informational Insecurity Is Not One Thing

Distrust erodes both tie types and erodes bridging ~`r sprintf("%.1f", h3c_row("J4_distrust")$strength_ratio_BSC_over_BoSC)`× harder; perceived threat erodes neither, and is *positively* associated with bridging for TV threat.

::: {.theory-box}
The mechanism is **not singular**. Which facet a reader has in mind decides whether informational insecurity looks like erosion or like mobilization — and a one-construct framework cannot even pose that question, because it has nowhere to put the difference.
:::

[A framework treating informational insecurity as a single construct cannot state that result, let alone explain it.]{.neon-cyan}

::: notes
1. [⏱ 0:50]
2. 把三個 RQ 放在一起看：RQ1 說 repertoire 讓兩個 facet 分化，且排序不同；RQ2 說這個分化大部分是不被調節的；RQ3 說兩個 facet 下游走向相反。
3. 讀者心裡想的是哪個 facet，決定了 informational insecurity 看起來像 erosion 還是像 mobilization。
4. 這就是這篇論文對傳播理論的貢獻：機制不是單一的。單一構念的框架連這個問題都問不出來，因為它沒有地方安放這個差異。
5. （Provenance 的揭露放在下一張，不要在這裡先講掉。）
:::

---

## What This Study Does and Does Not Claim {.smaller-content}

:::: {.columns}
::: {.column width="58%"}
#### Does

- **Repertoires differentiate both facets** — the 14-df block is significant on all `r nrow(h1a_h1b_omnibus)` outcomes, under both estimators. H1a and H1b supported.
- **The two facets do not order audiences the same way** — cluster 3 (`r clab(3)`) is elevated on all four threat facets yet sits at rank `r fm_row("J4_distrust", 3)$rank` of 15 in distrust. A one-construct account cannot produce that.
- **Media distrust erodes both tie types, and bridging ~`r sprintf("%.1f", h3c_row("J4_distrust")$strength_ratio_BSC_over_BoSC)`× harder** — H3a and H3c supported, design-robust on bridging.
- **Amplification and attenuation coexist** across repertoires — conditional cultivation's own boundary case, not a contradiction.
- **A fifteen-repertoire typology with a documented labeling protocol** — 30 replicates, agreement measured and reported, no ideological field.
- **H3a and H3b were pre-stated as genuine rivals and adjudicated** — strong inference, not HARKing.

These survived a filter built to kill them: an omnibus gate, reference-free corroboration, and a second estimator, applied **before** anything was allowed to count. The RQ2 funnel is the clearest illustration — `r n_sig_int` significant terms → `r n_corrob_w` corroborated → **`r n_interp` interpretable**.
:::
::: {.column width="42%"}
#### Does not

- **Provenance** — H1a, H2b, H3a, H3b carried forward; H1b, H2a, H2c, H3c exploration-derived; both readings of the distrust ranking post-hoc.
- **Design** — cross-sectional, self-report; longitudinal or trace data would model distress–exposure coevolution directly.
- **Partisan confounding** — party ID sits in only one pooled wave. Imputing it from aggregate outlet ideology is an **ecological inference** and would over-control the repertoire predictor itself. The labeling protocol makes the restraint structural: no ideological orientation is assigned at all.
:::
::::

[Most of what could have been claimed was discarded on purpose — that is what makes the left-hand column worth believing.]{.neon-cyan}

[Robinson (1950); Schuessler (1999); Platt (1964); Kerr (1998).]{.citation}

::: notes
1. [⏱ 1:10]
2. **這張投影片的重點是左邊，不是右邊。** 舊版把它做成一張道歉清單，這是錯的——嚴格性是「相信這些發現」的**理由**，不是需要致歉的東西。
3. 左邊六項快速帶過，語氣要肯定：兩個 facet 都被 repertoire 分化；兩個 facet 的排序不同；distrust 侵蝕兩種 tie，bridging 大約快 `r sprintf("%.1f", h3c_row("J4_distrust")$strength_ratio_BSC_over_BoSC)` 倍；放大與減弱並存；一個有記錄的標籤協定；H3a/H3b 事前就是競爭假設。
4. **然後停一下講那句話**：這些是通過了一個「為了殺死它們而設計的過濾器」之後還留下來的。omnibus gate、reference-free corroboration、第二個估計法——都在任何東西被允許算數**之前**就套用了。
5. RQ2 的漏斗是最清楚的例子：`r n_sig_int` 個顯著項 → `r n_corrob_w` 個被 corroborate → 只剩 `r n_interp` 個 interpretable。**大部分本來可以宣稱的東西，是被刻意丟掉的。**
6. 右邊三項照實講，不要拖：provenance（H1b、H2a、H2c、H3c 是 exploration-derived）；design（橫斷面、自陳）；partisan confounding。
7. Partisan 那一項要講到位：個人政黨傾向只在其中一波，我們拒絕用媒體的整體意識形態傾向去推算個人傾向——這是教科書等級的 ecological inference 問題，也會過度控制 repertoire 這個預測變項本身。標籤協定把這個限制變成結構性的：schema 完全沒有 ideological orientation 欄位。
8. **這張投影片不能被刪**——它是整場演講對 claim scope 的揭露，而且現在也是最後一次把貢獻講清楚的機會。
:::

---

## References {.tight .scrollable}

- Bennett, W. L., & Livingston, S. (2018). The disinformation order: Disruptive communication and the decline of democratic institutions. *European Journal of Communication, 33*(2), 122–139. https://doi.org/10.1177/0267323118760317
- Chadwick, A. (2017). *The hybrid media system* (2nd ed.). Oxford University Press.
- Skrzypczak, J. (2019). The effect of the "China factor" on Taiwan's media system security as an example of the "privatization and outsourcing" of censorship and propaganda in the digital age. *Przegląd Strategiczny*, (12), 353–365. https://doi.org/10.14746/ps.2019.1.22
- Chang, A. C., & Tang, Y.-C. (2023). The political foundation of mainstream media trust in East and Southeast Asia: A cross-national analysis. *Asian Politics & Policy, 15*(4), 585–604. https://doi.org/10.1111/aspp.12715
- Strömbäck, J., Tsfati, Y., Boomgaarden, H., Damstra, A., Lindgren, E., Vliegenthart, R., & Lindholm, T. (2020). News media trust and its impact on media use: Toward a framework for future research. *Annals of the International Communication Association, 44*(2), 139–156. https://doi.org/10.1080/23808985.2020.1755338
- Knudsen, E., Dahlberg, S., Iversen, M. H., Johannesson, M. P., & Nygaard, S. (2021). How the public understands news media trust: An open-ended approach. *Journalism, 23*(11), 2347–2363. https://doi.org/10.1177/14648849211005892
- DiMaggio, P., Nag, M., & Blei, D. (2013). Exploiting affinities between topic modeling and the sociological perspective on culture. *Poetics, 41*(6), 570–606. https://doi.org/10.1016/j.poetic.2013.08.004
- Grimmer, J., & Stewart, B. M. (2013). Text as data: The promise and pitfalls of automatic content analysis methods for political texts. *Political Analysis, 21*(3), 267–297. https://doi.org/10.1093/pan/mps028
- Pham, C. M., Hoyle, A., Sun, S., Resnik, P., & Iyyer, M. (2024). TopicGPT: A prompt-based topic modeling framework. In *Proceedings of NAACL-HLT 2024* (pp. 2956–2984). Association for Computational Linguistics. https://doi.org/10.18653/v1/2024.naacl-long.164
- Brin, S., Motwani, R., Ullman, J. D., & Tsur, S. (1997). Dynamic itemset counting and implication rules for market basket data. *ACM SIGMOD Record, 26*(2), 255–264. https://doi.org/10.1145/253262.253325
- Hahsler, M. (2015). *A probabilistic comparison of commonly used interest measures for association rules*. https://mhahsler.github.io/arules/docs/measures
- Lavrač, N., Flach, P., & Zupan, B. (1999). Rule evaluation measures: A unifying view (pp. 174–185). Springer Berlin Heidelberg. https://doi.org/10.1007/3-540-48751-4_17
- Monroe, B. L., Colaresi, M. P., & Quinn, K. M. (2008). Fightin' words: Lexical feature selection and evaluation for identifying the content of political conflict. *Political Analysis, 16*(4), 372–403. https://doi.org/10.1093/pan/mpn018
- Song, H., Kull, M., Flach, P., & Kalogridis, G. (2016). Subgroup discovery with proper scoring rules (pp. 492–510). Springer International Publishing. https://doi.org/10.1007/978-3-319-46227-1_31
- Tan, P.-N., Kumar, V., & Srivastava, J. (2004). Selecting the right objective measure for association analysis. *Information Systems, 29*(4), 293–313. https://doi.org/10.1016/s0306-4379(03)00072-3

::: notes
1. 這一頁與下一頁的引用來自 IIS-auto.bib，逐一核對過 citekey，也核對過每個引用是否真的支持它被掛上的那句話。
2. 後六筆是 slide「Naming Them」的測量文獻（added value / lift / subgroup discovery），來自 appendix S2.1。
:::

---

## References II {.tight .scrollable}

- Hetsroni, A. (2014). Ceiling effect in cultivation. *Journal of Media Psychology, 26*(1), 10–18. https://doi.org/10.1027/1864-1105/a000099
- Russell, C. A., & Buhrau, D. (2015). The role of television viewing and direct experience in predicting adolescents' beliefs about the health risks of fast-food consumption. *Appetite, 92*, 200–206. https://doi.org/10.1016/j.appet.2015.05.023
- Beaudoin, C. E. (2011). News effects on bonding and bridging social capital: An empirical study relevant to ethnicity in the United States. *Communication Research, 38*(2), 155–178. https://doi.org/10.1177/0093650210381598
- Leong, A. D., McComas, K. A., Balog-Way, D. H. P., & Schuler, K. L. (2023). Expanding on behavioral outcomes in the risk information seeking and processing model. *Science Communication, 45*(3), 310–336. https://doi.org/10.1177/10755470231165489
- Neyazi, T. A., Kalogeropoulos, A., & Nielsen, R. K. (2021). Misinformation concerns and online news participation among internet users in India. *Social Media + Society, 7*(2). https://doi.org/10.1177/20563051211009013
- Goodwin, R., Willson, M., & Stanley, G. (2005). Terror threat perception and its consequences in contemporary Britain. *British Journal of Psychology, 96*(4), 389–406. https://doi.org/10.1348/000712605x62786
- Hameleers, M., & Garnier Ortiz, M. (2024). Risk perceptions of misinformation exposure across platforms, issues, modalities, and countries: A comparative study across the Global North and South. *The International Journal of Press/Politics, 31*(2), 344–366. https://doi.org/10.1177/19401612241304050
- Matthes, J., Corbu, N., Jin, S., Theocharis, Y., Schemer, C., van Aelst, P., … Zoizner, A. (2022). Perceived prevalence of misinformation fuels worries about COVID-19: A cross-country, multi-method investigation. *Information, Communication & Society, 26*(16), 3133–3156. https://doi.org/10.1080/1369118x.2022.2146983
- Robinson, W. S. (1950). Ecological correlations and the behavior of individuals. *American Sociological Review, 15*(3), 351. https://doi.org/10.2307/2087176
- Schuessler, A. A. (1999). Ecological inference. *Proceedings of the National Academy of Sciences, 96*(19), 10578–10581. https://doi.org/10.1073/pnas.96.19.10578
- Platt, J. R. (1964). Strong inference. *Science, 146*(3642), 347–353. https://doi.org/10.1126/science.146.3642.347
- Kerr, N. L. (1998). HARKing: Hypothesizing after the results are known. *Personality and Social Psychology Review, 2*(3), 196–217. https://doi.org/10.1207/s15327957pspr0203_4

::: notes
1. 補充引用，涵蓋 ceiling effect、conditional cultivation、以及 ecological inference / HARKing 的方法論文獻。
:::

---

## {.closing .horizon .bleed style="--horizon-bottom: 10%;"}

::: {.kicker}
Insecure Island Syndrome · TCS 2022 + 2024
:::

::: {.thesis}
Informational insecurity is **[not one thing]{.thesis-key}**—and only one facet does the eroding.
:::

:::: {.columns}
::: {.column width="58%"}
::: {.ask}
Questions?
:::
:::
::: {.column width="42%"}
::: {.namecard}
#### Mu-Jung "MJ" Cho | 卓牧融
[mjcho@as.edu.tw]{.neon-red}

RCHSS, Academia Sinica

with Chia-Ming Hsu, RCHSS, Academia Sinica
:::
:::
::::

::: notes
1. 兩個 facet 一個侵蝕、一個沒有，甚至在某些情況下是正向的。
2. 這就是這場演講想留下的一句話：informational insecurity 不是一件事。
3. 歡迎提問。
:::

# Backup

---

## B1 — Full Cluster Taxonomy {.tight .scrollable}

```{r}
#| label: tbl-b1-taxonomy
cluster_taxonomy %>%
  transmute(Cluster = ifelse(id == 0, "0 (ref)", as.character(id)),
            `Label (EN)` = en, n) %>%
  knitr::kable()
```

`r cluster_labels_provisional_note`

::: notes
1. 完整十五列命名表，含樣本數；標籤仍為暫定版本。
:::

---

## B2 — Full RQ2 Verdict Table {.tight .scrollable}

```{r}
#| label: tbl-b2-rq2-verdict
rq2_verdict_table %>%
  transmute(
    Mediator = mediator,
    Moderator = ifelse(moderator == "N3_z", "Security", "Distress"),
    `F` = sprintf("%.2f", F_weighted),
    `p (wtd/design)` = paste0(sapply(p_weighted, fmt_pv), " / ", sapply(p_design, fmt_pv)),
    Concordant = ifelse(design_concordant, "yes", "no"),
    Gate = ifelse(omnibus_null, "closed", "OPEN")
  ) %>%
  knitr::kable()
```

::: notes
1. 全部十個 cell 的 omnibus gate 結果與 design concordance。
:::

---

## B3 — Full b-Path Coefficient Tables {.tight .scrollable}

```{r}
#| label: tbl-b3-pathb
label_map_b <- c(
  TV_threat = "TV Threat", Aggression_online = "Online Aggression",
  Disinfo_ops = "Disinfo Ops", xMedia_FakeNews = "xMedia FakeNews",
  Distress = "Psychological Distress (z)", J4_distrust = "Media Distrust",
  setNames(paste0("Cluster ", 1:14), paste0("cluster", 1:14))
)
path_b_table %>%
  mutate(Term = label_map_b[term]) %>%
  filter(!is.na(Term)) %>%
  transmute(term, Term, `Bridging SC` = sprintf("%.3f (%.3f)%s", estimate, std.error, sig)) %>%
  left_join(
    path_b_bosc_table %>%
      transmute(term, `Bonding SC` = sprintf("%.3f (%.3f)%s", estimate, std.error, sig)),
    by = "term"
  ) %>%
  select(-term) %>%
  knitr::kable()
```

Distress is strongly negative on bonding ($b$ `r fmt_est(coef_row_bosc("Distress")$estimate)`, $p$ `r fmt_p(coef_row_bosc("Distress")$p.value)`) but only marginal on bridging ($b$ `r fmt_est(coef_row("Distress")$estimate)`, $p$ `r fmt_p(coef_row("Distress")$p.value)`).

::: notes
1. 完整的 Path B 係數表，含 repertoire block；兩個結果變項是在完全相同的樣本上估計，係數可直接比較。
:::

---

## B4 — Measurement Detail {.tight .scrollable}

```{r}
#| label: tbl-b4-reliability
mediator_reliability_table %>%
  transmute(Mediator = mediator, `Cronbach's alpha` = round(alpha, 3)) %>%
  knitr::kable()
```

```{r}
#| label: tbl-b4-j4sens
j4_channel_sensitivity_table %>%
  transmute(
    Version = version, Outcome = outcome, N = format(N, big.mark = ","),
    `F (wtd)` = sprintf("%.2f", F_weighted),
    `p (wtd/design)` = paste0(sapply(p_weighted, fmt_pv), " / ", sapply(p_design, fmt_pv)),
    `H1b sig.` = ifelse(h1b_significant, "yes", "no")
  ) %>%
  knitr::kable()
```

Metric invariance: $\Delta\chi^2$(`r inv_row("configural_to_metric")$df_diff`) = `r sprintf("%.2f", inv_row("configural_to_metric")$chisq_diff)`, *p* `r fmt_p(inv_row("configural_to_metric")$p_value)`. Scalar vs. metric: $\Delta$CFI = `r fmt_nz(inv_row("metric_to_scalar")$delta_cfi)`.

::: notes
1. Mediator reliability、J4 頻道敏感性分析（complete-on-all-five 仍重現 H1b），以及 measurement invariance 的關鍵數字。
:::

---

## B5 — Design Concordance Ledger {.tight .scrollable}

`r design_concordance_headline`

```{r}
#| label: tbl-b5-concordance
design_concordance_summary %>%
  transmute(Block = block, Claim = claim, Primary = primary,
            `Design-based` = design_based, Status = status) %>%
  knitr::kable()
```

::: notes
1. 逐項列出主要估計法與 design-based 檢驗的一致性。
:::

---

## B6 — What the RQ2 Interaction Blocks Can Detect {.tight .scrollable}

```{r}
#| label: tbl-b6-mde
# Appendix v5.1 S4.2 REMOVED the old per-cell power table (min. detectable vs observed f2,
# with a "Powered" verdict) as post-hoc power reasoning. This backup slide now carries the
# design-property statement that replaced it: what the design can detect, full stop.
rq2_power_table %>%
  distinct(N, df1, df2, min_detectable_f2) %>%
  arrange(N) %>%
  transmute(
    `Interaction block` = ifelse(N == max(N),
                                 "Media-distrust cells (2 of 10)",
                                 "Threat-facet cells (8 of 10)"),
    N   = format(N, big.mark = ","),
    df  = paste0(df1, ", ", format(df2, big.mark = ",")),
    `Min. detectable f² (80% power, α = .05)` = sprintf("%.4f", min_detectable_f2)
  ) %>%
  knitr::kable()
```

The 14-df repertoire × moderator block detects $f^2 \ge$ `r sprintf("%.4f", min(rq2_power_table$min_detectable_f2))`–`r sprintf("%.4f", max(rq2_power_table$min_detectable_f2))` at 80% power, α = .05 — well below conventional small-effect benchmarks.

::: {.theory-box}
**A closed gate therefore rules out repertoire-level moderation of ordinary size.** Moderation smaller than that threshold is not ruled out, and we do not claim it is. This is a property of the **design**, stated and stopped there: comparing each cell's *observed* effect against its own minimum detectable effect would be post-hoc power reasoning — the observed effect and the *p*-value are two expressions of the same quantity, so the comparison cannot supply evidence the *p*-value did not already carry.
:::

[Design-effect check: `r design_effect_diagnostic$term[1]` SE ratio (design/lm) = `r sprintf("%.2f", design_effect_diagnostic$se_ratio[1])`. Appendix S4.2.]{.citation}

::: notes
1. 這張備用投影片回答的是「null 結果算不算證據」。
2. 答案來自 design，不是來自觀察到的效果量：14 df 的交互作用 block 在 80% power、α = .05 下可偵測到 f² 約 `r sprintf("%.4f", min(rq2_power_table$min_detectable_f2))` 以上，遠低於慣例的小效果標準。
3. 所以 gate 關閉＝排除了「一般大小」的 repertoire-level moderation；比這更小的調節效果沒有被排除，我們也不宣稱被排除。
4. **不要**把每個 cell 的 observed f² 拿來跟它自己的最小可偵測值比——那是 post-hoc power 推論，appendix v5.1 已經把那張表移除了。observed effect 與 p 值是同一件事的兩種表達。
:::

---

## B7 — Indirect Effects Through Media Distrust (cut from main deck) {.tight .scrollable}

**Descriptive.** The interpretable set is the **`r nrow(h3_distrust_indirect_table)`** unmoderated distrust-pathway indirect effects (14 repertoire contrasts × 2 outcomes). `r sum(h3_distrust_indirect_table$ind_sig)` significant under the primary bootstrap, `r sum(h3_distrust_indirect_table$design_sig)` design-robust: clusters 5 (`r clab(5)`), 6 (`r clab(6)`) and 10 (`r clab(10)`), **all on bridging**, each negative (e.g. cluster 10 $IE$ = `r sprintf("%.4f", ie_row("BSC", 10)$indirect)`, 95% CI `r fmt_ci(ie_row("BSC", 10)$ind_lo, ie_row("BSC", 10)$ind_hi, 4)`).

Counting significant conditional cells is not a test of moderated mediation; the appropriate test is an index of moderated mediation, which was not estimated and no claim rests on it.

[That all three survivors fall on bridging is consistent with the H3c result.]{.neon-cyan}

::: notes
1. [⏱ 0:40 — cut from the 18-minute main deck per §7; kept here for Q&A]
2. `r nrow(h3_distrust_indirect_table)` 個未被調節的 distrust indirect effect，其中 `r sum(h3_distrust_indirect_table$design_sig)` 個 design-robust，全部落在 bridging，且都是負向。
3. 這與 H3c 的結果一致，但不構成 moderated-mediation 的檢驗——我們沒有估計 index of moderated mediation。
:::

---

## B8 — Why This Isn't Just Measurement Noise (cut from main deck) {.tight .scrollable}

In-sample: media distrust correlates $r$ = `r fmt_nz(r_of("J4_distrust", "JB1_z"))` with the TV-side threat battery and $r$ = `r fmt_nz(r_of("J4_distrust", "JB2_z"))` with the online-side battery, while the two threat batteries correlate $r$ = `r fmt_nz(r_of("JB1_z", "JB2_z"))` with each other.

The stronger defence does not rest on our sample: **the media-trust ↔ perceived-threat association has no stable sign across studies** — Hameleers & Garnier Ortiz (2024) negative on trust, Neyazi et al. (2021) and Matthes et al. (2022) positive, every estimate weak (none exceeding |.17|).

[Instability of that kind is what two separable objects look like when each is measured with a different instrument in a different population.]{.neon-cyan}

::: notes
1. [⏱ 0:40 — cut from the 18-minute main deck per §7; kept here for Q&A]
2. 樣本內：distrust 與兩個威脅 battery 的相關都很弱，兩個威脅 battery 彼此的相關卻強得多。
3. 更關鍵的防線在樣本外：media trust 與 perceived threat 的關聯在跨研究中方向不穩定，三個研究、兩個方向，且都很弱。
4. 這種不穩定正是兩個各自被不同工具、不同母體測量的獨立構念該有的樣子。
:::

